---
title: "<span style='color:#fcab27'>Beautiful Tables in R</span>"
subtitle: "<span style='color:#3686d3'>gt and the grammar of tables</span> <br>"
author: "<a href = 'https://twitter.com/thomas_mock'><span style='color:#ff2b4f'>Tom Mock</span></a>"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    seal: false
    css: ["default", "css/my-theme.css", "css/my-fonts.css"]
    lib_dir: libs
    nature:
      beforeInit: "https://platform.twitter.com/widgets.js"
      ratio: '16:9'
      highlightStyle: dracula
      highlightLines: true
      countIncrementalSlides: false
      selfContained: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE, tibble.max_extra_cols = 6, tibble.width = 60)
knitr::opts_chunk$set(warning = FALSE, message = FALSE, fig.align = "center", dpi = 700)
library(tidyverse)
library(gt)
library(kableExtra)
library(xaringanExtra)
xaringanExtra::use_panelset()

```

```{r, echo=FALSE, cache=FALSE}
knitr::read_chunk('table-code.R')
```

```{r metathis, echo=FALSE}
library(metathis)
meta() %>%
  meta_name("github-repo" = "jthomasmock/tables-latinr") %>% 
  meta_social(
    title = "Beautiful tables in R with gt and the grammar of tables",
    description = paste(
      "Tables don't have to be boring,",
      "and can be created quickly and efficiently in R with gt!"
    ),
    url = "https://jthomasmock.github.io/tables-latinr",
    image = "https://raw.githubusercontent.com/jthomasmock/tables-latinr/master/images/title-card.png",
    image_alt = paste(
      "Title slide of 'Beautiful Tables in R, gt and the grammar of tables'.", 
      "A slide deck covering the basics of using gt and gtExtras.",
      "It also has a purple door with a stack of boxes stacked askew in front of it."
    ),
    og_type = "website",
    og_author = "Tom Mock",
    twitter_card_type = "summary_large_image",
    twitter_creator = "@thomas_mock",
    twitter_site = "@thomas_mock"
  )
```

class: title-slide, left, top

# `r rmarkdown::metadata$title`

## `r rmarkdown::metadata$subtitle`

### `r rmarkdown::metadata$author` `r fontawesome::fa("twitter", "#ff2b4f", height = "25px")`

### `r Sys.Date()`

<br>

`r fontawesome::fa("link", "white")` [jthomasmock.github.io/tables-latinr](https://jthomasmock.github.io/tables-latinr)   
`r fontawesome::fa("github", "white")` [github.com/jthomasmock/tables-latinr](https://github.com/jthomasmock/tables-latinr)  

<span style='color:white;'>Slides released under</span> [CC-BY 2.0](https://creativecommons.org/licenses/by/2.0/)&nbsp;&nbsp;`r fontawesome::fa("creative-commons", "white")``r fontawesome::fa("creative-commons-by", "white")` ]   

<div style = "position: absolute;top: 0px;right: 0;"><img src="https://images.unsplash.com/photo-1570554886111-e80fcca6a029?ixlib=rb-1.2.1&ixid=MnwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8&auto=format&fit=crop&w=1587&q=80" alt="A purple door with a stack of boxes stacked askew, falling to the left" width="460"></img></div>

---

```{r}
fontawesome::fa("twitter", "red", height = "23px")
```

